Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-09 report/report.tex
Table in-text references

The default minimum widths were obtained from (Lantmäteriet, 20). The standard minimum width for a two-lane road in Sweden is 6.5 meters.
Subsequent visual measurements of a few key locations in the Stockholm area revealed the following minimum way widths:

@@

% TODO: Interview with Todor
% TODO: Figure showing how turning function is calculated from edges and angles
% TODO: Figure refs, all figures
% TODO: Table numberings + references

>>>>

The default minimum widths were obtained from (Lantmäteriet, 20). The standard recommended minimum width for a two-lane road in Sweden is 6.5 meters.
Subsequent visual measurements of a few key locations in the Stockholm area revealed the following minimum way widths:
Table \ref{table:road-widths} shows the minimum and maximum road widths that were found during these measurements, and that will be used in the collision study.

@@

% TODO: Interview with Todor
% TODO: Figure showing how turning function is calculated from edges and angles
